\appendix

\chapter{Cycle 1 Student Interviews’ Questions and Feedback}
\label{app:cycle1_interviews}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Part 2
\section{Part 1: Background Information}

\scriptsize
\renewcommand{\arraystretch}{1.15}

\begin{longtable}{
|>{\RaggedRight\arraybackslash}p{3cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
}
\hline
\multicolumn{5}{|l|}{\textbf{Part 1: Background Information}} \\
\hline
\rowcolor{gray!15}
\multicolumn{1}{|c}{\textbf{Question}} & 
\multicolumn{2}{|c|}{\textbf{The Zanokhanyo Network}} & 
\multicolumn{2}{c|}{\textbf{Afrika Tikkun}} \\
\hline



1. Name & D & A1 & A2 & N1 \\
\hline

2. Surname & K & M & S & V \\
\hline

3. Date of Birth & 20/04/2016 (wrong) & 25/03/1980 & 11/6/1992 & 12/30/1993 \\
\hline

4. Where did you grow up? & Kinshasa & Democratic Republic of Congo & Eastern Cape & Cape Town \\
\hline

5. What is your highest level of qualification? & Diploma & Diploma & Grade 11 & Matric \\
\hline

6. What are your native or home languages? & French and Lingala & French & Xhosa & IsiXhosa \& English \\
\hline

7. How well do you speak English? & C. Conversant (Can hold extended conversations in English & C. Conversant (Can hold extended conversations in English & C. Conversant (Can hold extended conversations in English & C. Conversant (Can hold extended conversations in English \\
\hline

8. How well do you read in English? & G. Intermediate (Can read at secondary school level) & H. Advanced (Can read newspaper articles) & H. Advanced (Can read newspaper articles) & G. Intermediate (Can read at secondary school level) \\
\hline

9. How well can you write in English? & K. Intermediate (Can write emails) & I. Advanced (Can write essays, good knowledge of grammar) & I. Advanced (Can write essays, good knowledge of grammar) & I. Advanced (Can write essays, good knowledge of grammar) \\
\hline

10. What skills do you have? & Other: Electrician & Barista, Cooking, Computer/Typing, Computer-Microsoft Office, Computer-Internet, Driving, Other: Bartender, Waitron & Waiter, Childcare, Gardening, Computer - Microsoft Office, Computer - Internet, Accounting, Other - Salesman & Waiter, Barista, Cooking, driving: (Can drive but no license), Other: can listen properly) \\
\hline

11. What dependents do you have? & None & 1 Child & 2 children; but I haven't got a job and to me it causes depression & 2 children \\
\hline

\end{longtable}
\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Part 2
\section{Part 2: Understanding Participants and the Unemployment Problem}

\scriptsize
\renewcommand{\arraystretch}{1.15}

\begin{longtable}{
|>{\RaggedRight\arraybackslash}p{3cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
}
\hline
\multicolumn{5}{|l|}{\textbf{Part 2: Understanding Participants and the Unemployment Problem}} \\
\hline
\rowcolor{gray!15}
\multicolumn{1}{|c}{\textbf{Question}} & 
\multicolumn{2}{|c|}{\textbf{The Zanokhanyo Network}} & 
\multicolumn{2}{c|}{\textbf{Afrika Tikkun}} \\
\hline

1. Do you have a disability? 
& No 
& No 
& No 
& Yes \\
\hline

2. Do you currently have a job? 
& Yes 
& No 
& No 
& No \\
\hline

3. List your last 3 jobs, (if applicable):  
& Command security services, M.Z security, SAFRICAS Construction 
& Barista and Bartender, Stock controller, Chef cold salads  
& The waiter at Spar; Sales man selling fat cakes; Working as security temporarily 
& Waiter; Sales consultant; General worker at Home Choice (for example I will be reping [wrapping] boxes of Pick blanket form the floor to the boxes whereby they are being taked [taken] to the customer). \\
\hline

4. Why did you leave the jobs?  
& I did not earn enough money, I got a better job 
& I did not earn enough money, I lacked transportations money to my workplace, I did not like the job, I moved to another place, I got a better job, Other – I resigned 
& I did not earn enough money; The job was too difficult (be work at night and the cold); I did not like the job; I got a better job (When I worked in Spar I earned better money); Other (Contract ended [3 months]) 
& I was retrenched (end of contract); I got a better job (because I was working night shifts) \\
\hline

5. How did you find your jobs?  
& A friend told me about it, I found it myself 
& A friend of mine told me, rechecking to my phone, I sow at the new papper [paper]. 
& I put in CVs and going on internet to gamtree [Gumtree] or ask friends 
& From a community member \\
\hline

6. Have you tried to start your own business? If so, what kind? 
& Yes, I run a call centre (saling [selling] airtimes), saling clothes and shoes on credit 
& Yes / selling phones \& airtimes. I tried to open an internetcoffee [internet café] doesn’t work. I participated to open a coffee shop.  
& Yes, selling fat cakes; selling chips and mafints [muffins]; selling lollipes [lollipops] 
& Selling perfumes \\
\hline

7. How do you mostly search for a job?:  
& Ask my friends, use internet, walk and ask myself for jobs 
& Internet throw my phone. I walk through the restaurant, friends advertising. 
& Ask in friends and CVs 
& Doing door to door searching at malls; Malls \\
\hline

8. From what sources do you search for job openings?  
& Friends, Family, Gumtree, CVs, Other – give company my CV 
& Friends, Gumtree, walking into stores and asking/bulletin boards, NGOs/Organisations  
& Friends, Family, Other people, Gumtree, CVs, walking into stores and asking/bulletin boards, NGOs/Organisations 
& Friends, Family, Other people, Facebook, CVs, walking into stores and asking/bulletin boards. Other (Volunteer first then get the job later) \\
\hline

9. Will you be willing to travel to another place to find a job?  
& I travel from another country 
& Yes, I’m from Congo, I worked to supported [support] my struggling  
& Another city; Another country 
& Yes, Another city \\
\hline

10. What do you think will make you more employable (e.g. Types of skills/assistance/resources)?  
& Doing training – JR, basic electrical installations, fencing electric 
& Qualification 
& I need to have capital to start the business; I need to have proper business skill 
& Getting higher qualifications; getting myself a diploma or a degree \\
\hline

11. How do you make a living?  
& I have a job 
& N/A 
& I sell chips at home 
& No job but staying with my brother who is working \\
\hline

12. What kind of job do you want?  
& Electricity (like electrician), barista and bartending/waiter if I don’t get 1 
& I had sacing [saving] money I'm planning to have another experience so I'm willing 
& I want to start my own business 
& Business men \\
\hline

13. Would you like a short or long-term job?  
& A long one 
& I will prefer [prefer] a short term job 
& I want a long term job 
& long term \\
\hline

14. How often do you seek for jobs?  
& Asking friends who work in the field, drop my CV in the company, when I’m free because I have a job 
& Every day 
& I search ones [once] a week since I am attending a program so I haven't got time to seek for job; Every day before Afrika Tikkun 
& Twice after 2 weeks \\
\hline

15. How employable would you rate yourself (where 1 is not employable and 5 is very skilled or highly employable)?  
& 5 
& 5 
& 3 
& 3 \\
\hline

16. What is your best skill/qualification?  
& Diploma in international relations. I started a degree but I didn’t complete 
& Bartender and Barista 
& Sales man 
& Sales men, to sell \\
\hline

17. What will be your ideal job?  
& To be an officer administrator 
& I wanna run a restaurant 
& Selling good door to door 
& Owning my business \\
\hline

18. What skills do you need to get that job?  
& Complete my degree 
& I need people to support me, money, to advice me also 
& Business skills to start my own business, capital 
& Getting some skills first then find investors to invest on my business plan \\
\hline

\end{longtable}
\normalsize

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Part 3
\section{Part 3: Access and Usage of Technology}

\scriptsize
\renewcommand{\arraystretch}{1.15}

\begin{longtable}{
|>{\RaggedRight\arraybackslash}p{3cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
>{\RaggedRight\arraybackslash}p{2.7cm}|
}
\hline
\multicolumn{5}{|l|}{\textbf{Part 3: Access and Usage of Technology}} \\
\hline
\rowcolor{gray!15}
\multicolumn{1}{|c}{\textbf{Question}} & 
\multicolumn{2}{|c|}{\textbf{The Zanokhanyo Network}} & 
\multicolumn{2}{c|}{\textbf{Afrika Tikkun}} \\
\hline

1. Do you have a bank account? 
& Yes 
& No 
& No 
& Yes \\
\hline

2. How many phones do you own? 
& One 
& One 
& Non, my phones scrin [screen] damage 
& 1 \\
\hline

3. What type of phones do you have? 
& Blackberry 
& Table Galaxy 1, using as a phone 
& Non 
& Mobicel \\
\hline

4. Please bring and show any phones you have presently: 
& on charger 
&  
&  
& (Smart phone) android \\
\hline

5. Do you own a tablet? 
& No 
& Yes 
& No 
& No \\
\hline

6. Do you own a computer? 
& No 
& Yes 
& No 
& No \\
\hline

7. Do you borrow phones from others? 
& No 
& No 
& Yes 
& No \\
\hline

8. What purposes do you use a borrowed phone? 
& N/A 
& No 
& To go on watsup [WhatsApp] and phone my friends 
&  \\
\hline

9. Do you use call-backs/please call? 
& Yes, when I don't have airtime 
& Yes 
& Yes 
& No \\
\hline

10. Do you use missed calls? 
&  
& No 
& Yes 
& Yes \\
\hline

11. What purposes do you use missed calls? 
&  
& May the call that I missed was more important 
& Getting the person to call me back 
& When I don't have airtime to call \\
\hline

12. How many messages do you send? 
&  
& 3 per day 
& 5 times a day 
& 12 per week \\
\hline

13. How often do you make calls? 
& b. Every week 
& b. Every week (Note: 2 per day) 
& Everyday 
& Every week \\
\hline

14. Do you have an email address? 
& Yes 
& Yes 
& Yes 
& Yes \\
\hline

15. What is your email address? 
& \url{Dayl***@gmail.com} 
& \url{ange****@yahoo.com} 
& \url{AneleS****@gmail.com} 
& \url{Nkosa*****@gmail.com} \\
\hline

16. How often do you send emails? 
& c. Every month 
& c. Everyday (Note: Everyday via my phone) 
& It is new I haven't send emails yes. Opened it at Afrika Tikkuni 
& Every week \\
\hline

17. How frequently do you buy airtime and how much do you spend? 
& Every week 150 p/m 
& 2 times R20 a day 
& Twise [twice] after 2 days once every 2 days 
& Weekly R12 for \\
\hline

18. What features can you use on a phone? 
& Take pictures; Make calls; Send messages Use internet; Listen to music; Read PDF books 
& Send email; looking for jobs; calling friends/family; looking for news; Saving my own information - I have my CS, my bartending cocktails and chef recipes 
& Phoning; Sending massages [messages]; Sending call back; Going on Internet; Going on Facebook 
& Videorising [recording videos], Listening to music, Internet \\
\hline

19. What can you do with a phone (indicate all appropriate)? Understandability 
& Call; Send SMS; Take pictures; Chat on WhatsApp; Call on WhatsApp; Access Facebook; Record a video; Record a sound/song; Share sound/music 
& Call; Send SMS; Take pictures; Chat on WhatsApp; Call on WhatsApp; Record a video; Record a sound/song; Share sound/music (Note: yes but I don't do it) 
& Call; Send SMS; Take pictures; Chat on WhatsApp; Call on WhatsApp; Record a video; Record a sound/song; Share sound/music 
& Call, Send SMS, Take pictures, Chat on WhatsApp, Call on WhatsApp, Access Facebook, Record a video, Share sound/music \\
\hline

20. What are the most common things you do with a phone? 
& Call people (most common) 
& Looking for jobs; Some of cocktails I will like to take picture then I can recognized easily; FB; share < multimedia. 
& searching for jobs; to call < people>; take pictures; send call-backs; receive calls; SMS; FB; Note: I am using WhatsApp, I send pictures to my friends 
& Searching for jobs, to call < people> (make phone calls) \\
\hline

21. Are you aware of the job channel? 
& No 
& No 
& No 
& Yes \\
\hline

22. If yes, has it been useful? 
& N/A 
& N/A 
& N/A 
& No, because on those sites they need people with qualification which are high when I don't have \\
\hline

23. What programs are you aware of or have toy attended, e.g. Organisations/ NGOs 
& JR; Business communication; Diploma - international relations; Basic electrical installation and fencing electric 
& JR; Tourist management; Goldys; Short course: 2,5 months; Business communication; Diploma - international relations; Basic electrical installation and fencing electric 
& Afrika Tikkun 
& Afrika Tikkun (heard from a friend); NYDA -> HARAMBEE \\
\hline

24. What struggles do you face when looking for a job? 
& Information; as a security officer, sometimes I'm too busy with my job and I can't get information on time 
& Language; job may I ask me to speak Afrikaans. Ask me if I'm a citizen or Green I.D. 
& Money to travel to find jobs; Where to go and seek for J to find jobs (Note: He doesn't know where to find information) 
& Transportation; Professionalism; Lack of required skills and qualifications \\
\hline

\end{longtable}
\normalsize

\small \textit{Email addresses have been partially anonymised to protect participant identity.}