\chapter{Survey Instrument – Usability and Utility}
\label{app:survey_instrument}

%====================

\appsubsection{Background Information}

\begin{enumerate}
\item Which organisation have you attended JR classes:
\item When were you a part of the JR program?
\item How long was the JR program you attended?
\item How do you find jobs?
\item What device/phone do you have?
\item Do you use your device to search for jobs?
\item If so, how do you use your device to search for jobs?
\end{enumerate}

%====================

\appsubsection{JR Program}

\begin{enumerate}
\item Do you currently have a job?
\item How did you get your current job?
\item In what ways has the Afrika Tikkun/Zanokhanyo JR program assisted you? B
\item Has the JR program helped in getting a job? B
\end{enumerate}

%====================

\appsubsection{Khanya Job Network Utility Questions}

\begin{enumerate}
\item Is Khanya Job Network a useful tool for finding a job?
\item If yes, in what ways is it useful for you?
\item Is Khanya Job Network a useful tool for starting a business?
\item If yes, in what ways is it useful for you?
\item Would you use this application when looking for jobs?
\item Would you use this application to create a CV?
\item Would you recommend this application to others looking for a job?
\item Compare this application to another application you have used before.
\item Have you used indeed.com, gumtree and giraffe did they support you well for finding jobs (did they do what you wanted)?
\item Were the jobs sent to you relevant to your skills and qualifications? A
\end{enumerate}

%====================

\appsubsection{Khanya Job Network Usability Questions}

\begin{enumerate}
\item How easy is it to perform the registration process?
\item How easy is it to log in to Khanya Job Network?
\item How easy is it to edit your CV?
\item How easy is it to download your CV to an employer?
\item What is your favourite feature from Khanya Job Network?
\item What feature would you like improved?
\item How easily do you believe Khanya Job Network would help you get a job?
\item Were the job finding, CV and interview tips useful?
\item How understandable were the words used in the registration process?
\end{enumerate}

%====================

\appsubsection{SMS/Email Vacancies Questions (Utility and Usability)}

\begin{enumerate}
\item Which means of notification have you chosen if any?
\begin{enumerate}\item Why?\end{enumerate}
\item If any notification/s chosen:

\begin{enumerate}
\item Were the jobs found a good match to the skills/qualifications you have? A
\item Have you been invited to a job interview?
\item Did you receive SMS/email or both notifications?
\begin{enumerate}
\item If making use of Email: Was the vacancies information on the email useful?
\item If making use of SMS: Was the vacancies information sent via SMS useful?
\end{enumerate}
\end{enumerate}
\end{enumerate}